Are We Reusing Outdated and License-violating Code \newline from Stack Overflow?

### 2017-01-26 cloneoverflow-latex/cloneoverflow.tex
Changed the diagram of good/ok pairs to horizontal bar charts.
- fixed the number in Table 6 to be back to they were before adding missing ND projects (to avoid confusion). They'll be put back in when everything is done.

\vspace{0.5ex}%
\noindent\textbf{1.~A manual study of online code clones:} 
We used two clone detection tools to discover 270,429,422 similar code fragment pairs and manually investigated 3,450 candidate clone pairs between Java code fragments obtained from Stack Overflow accepted answers and 111 Java open source projects.

@@

\begin{figure*}
	\centering
	\includegraphics[width=0.8\linewidth]{exp_framework}
	\caption{Experimental framework}
	\label{fig:exp_framework}
\end{figure*}

\subsection{Experimental Framework}
To answer the four research questions, we followed the experimental framework depicted in \Cref{fig:exp_framework}. We processed two datasets, Stack Overflow and 111 open source projects from Qualitas corpus. Java code fragments were extracted from Stack Overflow posts using regular expressions. We prepared Java code in both datasets by removing comments and pretty-printing to increase accuracy of clone detection. Then, we deployed two clone detection tools, Simian \cite{simian} and NiCad \cite{Roy2008,Cordy}, to locate clones between the two datasets. Due to scalability of Simian and NiCad, we partitioned the input and run the tools multiple times. Each run was composed of the whole Stack Overflow data and single Qualitas project. We repeated the process until we cover 111 projects.

@@

\begin{table*}
	\centering
	\caption{The number of online clone pair condidates (mutually exclusive) before and after filtering. The last column shows the number of true positive clone pairs after the manual investigation. }
	\label{tab:online_clone_pairs}
	\small
	\begin{tabular}{l|r|c|c|c|c|r|r|r|r}
		\hline
		\multirow{2}{*}{Clone set} & \multicolumn{1}{c|}{Before} & \multicolumn{4}{c|}{Filters*} & \multirow{2}{*}{Candidates} & \multirow{2}{*}{\texttt{equals()}} & \multirow{2}{*}{Manual} & \multirow{2}{*}{TP} \\ \cline{3-6}
		        		  & \multicolumn{1}{c|}{Filters} & \textit{L} & \textit{S} & \textit{R} & \textit{G} & & & & \\
		\hline 
		\multirow{1}{*}{\textit{good}} & & & & & & 2,261 & 9 & 2,252 & 72 \\
		\multirow{1}{*}{\textit{ok}} &  & & & & & 9,322 & 9,122 & 200 & 9,240 \\
		%\multirow{1}{*}{\textit{agreed clone pairs}}      & 29,099 \\
		\multirow{1}{*}{$S_D$} & 67,570 & \checkmark & & \checkmark & \checkmark & 17,801 & 16,930 & 871 & 704 \\
		\multirow{1}{*}{$N_D$} & 229,176 & & \checkmark & \checkmark & \checkmark & 168 & 41 & 127 & 116 \\ 
		%\multirow{1}{*}{\textit{disagreed clone pairs}}    & 1,039 \\
		\hline
		Total  & 296,746 & & & & & 47,068 & 26,102 & 3,450 & 10,132 \\ 
		\hline
	 	\multicolumn{10}{l}{\scriptsize{Filters*: \textit{L}=$Line \geq 10$, \textit{S}=$Sim \geq 80\%$, \textit{R}=regular expressions, and \textit{G}=\textit{good}/\textit{ok} pairs.}}
	\end{tabular} 
\end{table*}

The clone statistics obtained from running Simian and NiCad with \textit{D} and \textit{E} configurations are presented in \Cref{tab:raw_stats}. From \Cref{tab:raw_stats}, Simian clones cover approximately 10\% of the 144,075 Stack Overflow snippets, 1,086 reported by $S_D$ and 1,530 from $S_E$ respectively. $N_D$ reports clones in 1,240 Stack Overflow code snippets, while $N_E$ reports clones in a larger number of 12,886 snippets  mainly due to its relaxed configurations. In terms of number of clone pairs, $S_E$ and $N_E$ report a large number of clone pairs of 63,372,599 and 206,760,077 respectively. This is expected since EvaClone configurations prefer recall so it tends to remote more clones \cite{Wang2013}. The average clone size of$S_D$ is 7.72 lines which is bigger than its $S_E$ counterpart of 4.79. Similarly, $N_D$ has an average clone size of 9.64 lines which is bigger than 5.32 reported by $N_E$. We can see from the statistics that EvaClone tunes the tools in the way that they report smaller clones. The average percentage of Stack Overflow code snippets that are cloned according to$S_D$, $S_E$, $N_D$, and $N_E$ is 29\%, 28\%, 25\%, and 21\% accordingly. Preliminary manual investigation of Simian's clone report revealed that there were problematic 11 fragments. These 11 fragments triggered Simian to generate large clone clusters containing a huge number of false clones from array initialisation. Hence, their clones were removed from further analyses.

@@

@@

Agreed clone pairs are clone pairs that pass Bellon's good- or ok-match criteria and selected for manual investigation. Similar to the original study, we select a threshold \textit{p} of 0.7 for both \textit{good} and \textit{ok} pairs \cite{Bellon2007}. %The number of projects processed by the clone detection tools are listed in \Cref{tab:projects_missing}. 
We encountered NiCad failures with a few Qualitas projects. 
%\FIXME{Reported the errors to NiCad creator. Cordy said it might be a long-path problem. Should we try fixing?}  
$N_D$ could not detect clones in Hibernate due to clustering errors. $N_E$ generated renaming errors for 5 projects including Vuze, Hibernate, Myfaces, Netbeans, and Spring. We had contacted the author of NiCad regarding the issues. They found that there problems of long file paths and TXL grammars which will be fixed in the next NiCad releases. As a result, we did not have NiCad clones from these project in the agreed clone pairs. Simian clones of the same projects also disappeared from the agreed clone pairs since they could not find matches.

\begin{table}
	\centering
	\caption{No.~of successfully analysed Qualitas projects}
	\label{tab:projects_missing}
	\small
	\begin{tabular}{l|r|r|r|r}
		\hline
		Execution & $S_D$ & $S_E$  & $N_D$ & $N_E$ \\ 
		\hline
		\textit{Successful} & 111 & 111 & 100 & 96 \\ 
		\textit{Clustering fail} & -- & -- & 1 & -- \\
		\textit{Renaming fail} & -- &  -- & -- & 5 \\
		\hline
	\end{tabular}
\end{table}

\begin{table}
	\centering
	\caption{Distribution of agreed clone pairs}
	\label{t_agreed_good_clone_pairs}
	\small
	\resizebox{\columnwidth}{!}{%
	\begin{tabular}{l|r|r|r|r|r|r}
		\hline
		Set & $S_DN_D$ & $S_DN_E$ & $S_EN_D$ & $S_EN_E$ & Total & Unique \\
		\hline
		\textit{good} & 10 & 26 & 10 & 2,228 & 2,321 & 2,308 \\
		\textit{ok} & 9,042 & 991 & 78 & 17,549 & 27,670 & 26,838 \\
		\hline
	\end{tabular} %
}
\end{table}

The distributions of \textit{good} clone pairs between four combinations of \textit{D} and \textit{E} configurations are listed in \Cref{t_agreed_good_clone_pairs} and depicted visually in \Cref{fig:venn4_orig_good}. There are 2,261 unique \textit{good} pairs consisting of 10 pairs from $S_DN_D$, 26 pairs from $S_DN_E$, 10 pairs from $S_EN_D$, and 2,228 pairs from $S_EN_E$. There are 26,838 unique \textit{ok} pairs (excluding the subsumed 2,261 \textit{good} pairs).\footnote{According to the definition, \textit{ok} clone pairs always subsume the \textit{good} pairs.} We obtained 9,052; 991; 78; and 17,549 pairs from $S_DN_D$, $S_DN_E$, $S_EN_D$, and $S_EN_E$ respectively. Between the four configuration sets, there are considerable amount of clone pairs shared between two adjacent sets (as depicted in \Cref{fig:venn4_orig_ok}), but there is no clone pair that is agreed by all four combinations. %If we remove duplicates, the number of unique ok-match pairs is 26,838.

@@

\begin{figure*}
	\begin{minipage}{.5\textwidth}
		\centering
		\includegraphics[width=0.7\linewidth]{venn4_pairs_good_pt1+2+3+fixed_nicad-crop}
		\caption{Distributions of \textit{good} pairs}
		\label{fig:venn4_orig_good}
	\end{minipage}
	\begin{minipage}{.5\textwidth}
		\centering
		\includegraphics[width=0.7\linewidth]{venn4_pairs_ok_pt1+2+3+fixed_nicad-crop}
		\caption{Distributions of \textit{ok} pairs}
		\label{fig:venn4_orig_ok}
	\end{minipage}
\end{figure*}

@@

In our manual investigation process, we used a script to automatically classify \texttt{equals()} clone pairs which helped classifying 26,102 pairs out of 47,068 (more than half of the \texttt{equals()} pairs came from $S_D$). Finally, there are 3,450 pairs remaining which we manually investigated them. \textbf{To answer RQ1, we found 47,068 clone candidates between 111 Qualitas projects and 144,075 Stack Overflow snippets. They are 2,261 \textit{good} pairs, 26,838 \textit{ok} pairs. XXX After a manual investigation, we found at least 523 online code clones pairs are true clones.}

@@

We started by studying the 8 patterns of cloning from Kapser et al.~\cite{Kapser2006,Kapser2008}. We use the patterns to classify 697 clone pairs associated with 34 sampled Stack Overflow fragments. This preliminary investigation aims to evaluate the applicability of Kapser's cloning patterns to our study. Using$S_D$ clone report, fragments are ranked according to (1) frequency, (2) popularity (i.e.~number of associated Qualitas projects), (3) clone size in SLOC, and (4) clone percentage compared to the fragment size. We then picked the top 10 fragments from the 4 groups resulting in 34 Stack Overflow fragments chosen (there were some overlaps). The 34 selected snippets generate 697 clone pairs. Using Kapser's cloning patterns, the 697 clone pairs were categorised into either Customisation or Templating. Clearly \textbf{Kapser's cloning patterns are too broad for our study and a more suitable and fine-grained classification scheme is needed.}

@@

\subsubsection{Manual Investigation of Clone Candidates}

The first author who has been working on clone detection research for two years takes the role of a main investigator performing manual investigation of all 3,450 clone pairs. The third author takes the role of a second investigator performing 10\% validation of the clone pairs judged by the main investigator. Following the cloning patterns, the main investigator manually goes through each agreed clone pair, looks at the clones, and chooses the most appropriate cloning pattern for the pair. A relevant and useful observation is also recorded for each clone pair.

@@

\begin{figure*}
	\begin{lstlisting}
/* Code in Stack Overflow #23520731 */     /* SchemaUpdate.java (2016-09-26) */
public void execute (Target target) {      public void execute(EnumSet<TargetType> targetTypes, 
  LOG.runningHbm2ddlSchemaUpdate();                        Metadata metadata, ServiceRegistry serviceRegistry) {
  Connection connection = null;              if ( targetTypes.isEmpty() ) {
  Statement stmt = null;                       LOG.debug(""Skipping SchemaExport as no targets were specified"");
  Writer outputFileWriter = null;              return;
  exceptions.clear();                        }
  try {                                      exceptions.clear();
    DatabaseMetadata meta;                   LOG.runningHbm2ddlSchemaUpdate();
    ...                                      ...
	\end{lstlisting}
	\caption{Outdated code fragment on Stack Overflow post 23520731. This code has been copied from SchemaUpdate.java and its latest version in hibernate code base contains heavy modifications.}
	\label{fig:hibernate_outdated_code}
\end{figure*}

@@

\textbf{Software licensing} is crucial for open source and industrial software development. Di Penta et al.~study an evolution of software licensing in six FOSS and found that licensing statements change over time \cite{DiPenta2010}. German et al.~\cite{German2009} performed an empirical study of code siblings (code clones among different systems coming from the same source) and found that licensing conflicts can occur between the clone siblings. Later, German et al.~\cite{German2010} created Ninka, a tool to automate identification of software license from program source code. We use Ninka to analyse software license from Stack Overflow fragments and Qualitas projects.

@@

The work that is closely similar to us is a study by An et al.~\cite{An2017}. The authors investigated clones between 399 Android apps and Stack Overflow posts. They found 1,226 code snippets which were reused from 68 Android apps. They also observed that there are 1,219 cases of potential license violations. However, the authors rely on the timestamp to judge whether the code has been copied from/to Stack Overflow along with confirmations from six developers. Instead of Android apps, we investigated clones between Stack Overflow and 111 open source projects. Our results confirm their findings that there are clones from software projects to Stack Overflow with potential licensing violations. In our work, we defined seven patterns of online code cloning and performed a large-scale manual check of 3,450 clone pairs. We discovered 96 clone pairs with strong evidences, based on natural text in comments and post contents, that they were copied from Qualitas to Stack Overflow. By comparing the clones to their latest versions in the software, we found that 58 code fragments on Stack Overflow are outdated and harmful for reuse.

>>>>

\vspace{0.5ex}%
\noindent\textbf{1.~A manual study of online code clones:} 
We used two clone detection tools to discover 270,429,422 similar code snippet pairs and manually investigated 3,450 candidate clone pairs between Java code snippets obtained from Stack Overflow accepted answers and 111 Java open source projects.

@@

\begin{figure}
	\centering
	\includegraphics[width=\linewidth]{exp_framework_new}
	\caption{Experimental framework}
	\label{fig:exp_framework}
\end{figure}

\subsection{Experimental Framework}
To answer the four research questions, we followed the experimental framework depicted in \Cref{fig:exp_framework}. We processed two datasets, Stack Overflow and 111 open source projects from Qualitas corpus. Java code snippets were extracted from Stack Overflow posts using regular expressions. We prepared Java code in both datasets by removing comments and pretty-printing to increase accuracy of clone detection. Then, we deployed two clone detection tools, Simian \cite{simian} and NiCad \cite{Roy2008,Cordy}, to locate clones between the two datasets. Due to scalability of Simian and NiCad, we partitioned the input and run the tools multiple times. Each run was composed of the whole Stack Overflow data and single Qualitas project. We repeated the process until we cover 111 projects.

@@

The clone statistics obtained from running Simian and NiCad with \textit{D} and \textit{E} configurations are presented in \Cref{tab:raw_stats}. From \Cref{tab:raw_stats}, Simian clones cover approximately 10\% of the 144,075 Stack Overflow snippets, 1,086 reported by $S_D$ and 1,530 from $S_E$ respectively. $N_D$ reports clones in 1,240 Stack Overflow code snippets, while $N_E$ reports clones in a larger number of 12,886 snippets  mainly due to its relaxed configurations. In terms of number of clone pairs, $S_E$ and $N_E$ report a large number of clone pairs of 63,372,599 and 206,760,077 respectively. This is expected since EvaClone configurations prefer recall so it tends to remote more clones \cite{Wang2013}. The average clone size of $S_D$ is 7.72 lines which is bigger than its $S_E$ counterpart of 4.79. Similarly, $N_D$ has an average clone size of 9.64 lines which is bigger than 5.32 reported by $N_E$. We can see from the statistics that EvaClone tunes the tools in the way that they report smaller clones. The average percentage of Stack Overflow code snippets that are cloned according to $S_D$, $S_E$, $N_D$, and $N_E$ is 29\%, 28\%, 25\%, and 21\% accordingly. Preliminary manual investigation of Simian's clone report revealed that there were problematic 11 snippets. These 11 snippets triggered Simian to generate large clone clusters containing a huge number of false clones from array initialisation. Hence, their clones were removed from further analyses.

@@

\begin{table}
	\centering
	\caption{The number of online clone pair condidates (mutually exclusive) before and after filtering.}
	\label{tab:online_clone_pairs}
	\small
%	\resizebox{\columnwidth}{!}{%
	\begin{tabular}{l|r|c|c|c|c|r}
		\hline
		\multirow{2}{*}{Set} & \multicolumn{1}{c|}{Before} & \multicolumn{4}{c|}{Filters*} & \multirow{2}{*}{Cand.} \\ \cline{3-6}
		& \multicolumn{1}{c|}{Filters} & \textit{L} & \textit{S} & \textit{R} & \textit{G} & \\
		\hline 
		\multirow{1}{*}{\textit{good}} & 2,261 & & & & & 2,261 \\
		\multirow{1}{*}{\textit{ok}} & 9,322 & & & & & 9,322 \\
		%\multirow{1}{*}{\textit{agreed clone pairs}}      & 29,099 \\
		\multirow{1}{*}{$S_D$} & 67,570 & \checkmark & & \checkmark & \checkmark & 17,801 \\
		\multirow{1}{*}{$N_D$} & 229,176 & & \checkmark & \checkmark & \checkmark & 168 \\ 
		%\multirow{1}{*}{\textit{disagreed clone pairs}}    & 1,039 \\
		\hline
		Total  & 296,746 & & & & & 28,832 \\ 
		\hline
		\multicolumn{7}{l}{\scriptsize{Filters*: \textit{L}=$Line \geq 10$, \textit{S}=$Sim \geq 80\%$,}} \\
		\multicolumn{7}{l}{\scriptsize{\textit{R}=regular expressions, and \textit{G}=\textit{good}/\textit{ok} pairs.}} \\
	\end{tabular} %
%}
\end{table}

\begin{table}
	\centering
	\caption{The online clone classification results}
	\label{tab:online_clone_pairs}
	\small
	%	\resizebox{\columnwidth}{!}{%
	\begin{tabular}{l|r|r|r|r}
		\hline
		\multirow{2}{*}{Set} & \multirow{2}{*}{Candidates} & \multicolumn{2}{c|}{Classification} & \multirow{2}{*}{TP} \\ \cline{3-4}
		& & Auto & Manual & \\
		\hline 
		\multirow{1}{*}{\textit{good}} & 2,261 & 9 & 2,252 & 72 \\
		\multirow{1}{*}{\textit{ok}} & 9,322 & 9,122 & 200 & 9,240 \\
		%\multirow{1}{*}{\textit{agreed clone pairs}}      & 29,099 \\
		\multirow{1}{*}{$S_D$} & 17,801 & 16,930 & 871 & 704 \\
		\multirow{1}{*}{$N_D$} & 168 & 41 & 127 & 116 \\ 
		%\multirow{1}{*}{\textit{disagreed clone pairs}}    & 1,039 \\
		\hline
		Total  & 28,832 & 26,102 & 3,450 & 10,132 \\ 
		\hline
	\end{tabular} %
	%}
\end{table}

@@

Agreed clone pairs are clone pairs that pass Bellon's good- or ok-match criteria and selected for manual investigation. Similar to the original study, we select a threshold \textit{p} of 0.7 for both \textit{good} and \textit{ok} pairs \cite{Bellon2007}. %The number of projects processed by the clone detection tools are listed in \Cref{tab:projects_missing}. 
We encountered NiCad failures with a few Qualitas projects. 
%\FIXME{Reported the errors to NiCad creator. Cordy said it might be a long-path problem. Should we try fixing?}  
$N_D$ could not detect clones in Hibernate due to clustering errors. $N_E$ generated renaming errors for 5 projects including Vuze, Hibernate, Myfaces, Netbeans, and Spring. We had contacted the creator of NiCad regarding the issues. They identified them as problems of long file paths and TXL grammars which will be fixed in the next NiCad releases. As a result, we did not have NiCad clones from these project in the agreed clone pairs. Simian clones of the same projects also disappeared from the agreed clone pairs since they could not find matches.

%\begin{table}
%	\centering
%	\caption{No.~of successfully analysed Qualitas projects}
%	\label{tab:projects_missing}
%	\small
%	\begin{tabular}{l|r|r|r|r}
%		\hline
%		Execution & $S_D$ & $S_E$  & $N_D$ & $N_E$ \\ 
%		\hline
%		\textit{Successful} & 111 & 111 & 100 & 96 \\ 
%		\textit{Clustering fail} & -- & -- & 1 & -- \\
%		\textit{Renaming fail} & -- &  -- & -- & 5 \\
%		\hline
%	\end{tabular}
%\end{table}

\begin{table}
	\centering
	\caption{Distribution of the agreed clone pairs}
	\label{t_agreed_good_clone_pairs}
	\small
	\resizebox{\columnwidth}{!}{%
	\begin{tabular}{l|r|r|r|r|r|r}
		\hline
		Set & $S_DN_D$ & $S_DN_E$ & $S_EN_D$ & $S_EN_E$ & Total & Unique \\
		\hline
		\textit{good} & 10 & 26 & 10 & 2,228 & 2,274 & 2,261 \\
		\textit{ok} & 9,049 & 993 & 79 & 19,777 & 29,898 & 29,058 \\
		\hline
	\end{tabular} %
}
\end{table}

\begin{figure}
	\centering
	\includegraphics[width=\linewidth]{good-ok_pairs-crop}
	\caption{Distribution of \textit{good} (top) and \textit{ok} pairs (bottom) in 4 configurations of Simian and NiCad. The shaded areas are overlapping pairs.}
	\label{fig:good-ok-pairs}
\end{figure}

The distributions of \textit{good} clone pairs between four combinations of \textit{D} and \textit{E} configurations are listed in \Cref{t_agreed_good_clone_pairs} and depicted visually in \Cref{fig:good-ok-pairs}. There are 2,261 unique \textit{good} pairs consisting of 10 pairs from $S_DN_D$, 26 pairs from $S_DN_E$, 10 pairs from $S_EN_D$, and 2,228 pairs from $S_EN_E$. There are 26,838 unique \textit{ok} pairs (excluding the subsumed 2,261 \textit{good} pairs).\footnote{According to the definition, \textit{ok} clone pairs always subsume the \textit{good} pairs.} We obtained 9,052; 991; 78; and 17,549 pairs from $S_DN_D$, $S_DN_E$, $S_EN_D$, and $S_EN_E$ respectively. Between the four configuration sets, there are considerable amount of clone pairs shared between two adjacent sets (as depicted in \Cref{fig:good-ok-pairs}), but there is no clone pair that is agreed by all four combinations. %If we remove duplicates, the number of unique ok-match pairs is 26,838.

@@

%\begin{figure*}
%	\begin{minipage}{.5\textwidth}
%		\centering
%		\includegraphics[width=0.7\linewidth]{venn4_pairs_good_pt1+2+3+fixed_nicad-crop}
%		\caption{Distributions of \textit{good} pairs}
%		\label{fig:venn4_orig_good}
%	\end{minipage}
%	\begin{minipage}{.5\textwidth}
%		\centering
%		\includegraphics[width=0.7\linewidth]{venn4_pairs_ok_pt1+2+3+fixed_nicad-crop}
%		\caption{Distributions of \textit{ok} pairs}
%		\label{fig:venn4_orig_ok}
%	\end{minipage}
%\end{figure*}

@@

In our manual investigation process, we used a script to automatically classify \texttt{equals()} clone pairs which helped classifying 26,102 pairs out of 47,068 (more than half of the \texttt{equals()} pairs came from $S_D$). Finally, there are 3,450 pairs remaining which we manually investigated them. \textbf{To answer RQ1, we found 47,068 clone candidates between 111 Qualitas projects and 144,075 Stack Overflow snippets. They are 2,261 \textit{good} pairs, 26,838 \textit{ok} pairs. After classification, we found at least 523 online code clones pairs that are true clones between Stack Overflow and Qualitas.}

@@

We started by studying the 8 patterns of cloning from Kapser et al.~\cite{Kapser2006,Kapser2008}. We use the patterns to classify 697 clone pairs associated with 34 sampled Stack Overflow snippets. This preliminary investigation aims to evaluate the applicability of Kapser's cloning patterns to our study. Using$S_D$ clone report, snippets are ranked according to (1) frequency, (2) popularity (i.e.~number of associated Qualitas projects), (3) clone size in SLOC, and (4) clone percentage compared to the snippet size. We then picked the top 10 snippets from the 4 groups resulting in 34 Stack Overflow snippets chosen (there were some overlaps). The 34 selected snippets generate 697 clone pairs. Using Kapser's cloning patterns, the 697 clone pairs were categorised into either Customisation or Templating. Clearly \textbf{Kapser's cloning patterns are too broad for our study and a more suitable and fine-grained classification scheme is needed.}

@@

\subsubsection{Classification of Clone Candidates}

There were 28,832 online clone pair candidates for classifications as shown in \Cref{tab:online_clone_pairs}. We have use regular expressions to automatically classify \texttt{equals()} methods based on the method signature since they are not very interesting clones. It captured 26,102 clone pairs and classified them into pattern D. With help of the automatic classification, there were 3,450 pairs left for manual classification.

The first author who has been working on clone detection research took the role of a main investigator performing manual classification of all the 3,450 clone pairs. The second author took the role of a second investigator performing 10\% validation of the clone pairs (345 pairs) judged by the main investigator. By consulting the cloning patterns, the main investigator manually went through each agreed clone pair, looked at the clones, and chose the most appropriate cloning pattern for the pair. A relevant and useful observation was also recorded for each clone pair. The two investigators discussed and resolved 51 classification conflicts. There are three conflicts which the investigators could not find consensuses hence the third author was involved to solve the conflicts.

@@

\begin{figure*}
	\begin{lstlisting}
/* Code in Stack Overflow #23520731 */     /* SchemaUpdate.java (2016-09-26) */
public void execute (Target target) {      public void execute(EnumSet<TargetType> targetTypes, 
  LOG.runningHbm2ddlSchemaUpdate();                        Metadata metadata, ServiceRegistry serviceRegistry) {
  Connection connection = null;              if ( targetTypes.isEmpty() ) {
  Statement stmt = null;                       LOG.debug(""Skipping SchemaExport as no targets were specified"");
  Writer outputFileWriter = null;              return;
  exceptions.clear();                        }
  try {                                      exceptions.clear();
    DatabaseMetadata meta;                   LOG.runningHbm2ddlSchemaUpdate();
    ...                                      ...
	\end{lstlisting}
	\caption{Outdated code snippet on Stack Overflow post 23520731. This code has been copied from SchemaUpdate.java and its latest version in hibernate code base contains heavy modifications.}
	\label{fig:hibernate_outdated_code}
\end{figure*}

@@

\textbf{Software licensing} is crucial for open source and industrial software development. Di Penta et al.~study an evolution of software licensing in six FOSS and found that licensing statements change over time \cite{DiPenta2010}. German et al.~\cite{German2009} performed an empirical study of code siblings (code clones among different systems coming from the same source) and found that licensing conflicts can occur between the clone siblings. Later, German et al.~\cite{German2010} created Ninka, a tool to automate identification of software license from program source code. We use Ninka to analyse software license from Stack Overflow snippets and Qualitas projects.

@@

The work that is closely similar to us is a study by An et al.~\cite{An2017}. The authors investigated clones between 399 Android apps and Stack Overflow posts. They found 1,226 code snippets which were reused from 68 Android apps. They also observed that there are 1,219 cases of potential license violations. However, the authors rely on the timestamp to judge whether the code has been copied from/to Stack Overflow along with confirmations from six developers. Instead of Android apps, we investigated clones between Stack Overflow and 111 open source projects. Our results confirm their findings that there are clones from software projects to Stack Overflow with potential licensing violations. In our work, we defined seven patterns of online code cloning and performed a large-scale manual check of 3,450 clone pairs. We discovered 96 clone pairs with strong evidences, based on natural text in comments and post contents, that they were copied from Qualitas to Stack Overflow. By comparing the clones to their latest versions in the software, we found that 58 code snippets on Stack Overflow are outdated and harmful for reuse.
